**NAME OF THIS STUDY**

### 2019-10-11 submission/manuscript.Rmd
Further optimization of the process

---
title: "**NAME OF THIS STUDY**"
bibliography: references.bib
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
csl: mbio.csl #Get themes at https://github.com/citation-style-language/styles
fontsize: 11pt
geometry: margin=1.0in
---

>>>>

---
title: "**NAME OF THIS STUDY**"
bibliography: references.bib
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
csl: citation_style.csl #Get themes at https://github.com/citation-style-language/styles
fontsize: 11pt
geometry: margin=1.0in
---
